% ------------------------------------------------------------------------ %
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = pdflatex
% !TEX root = ../Tesi.tex
% !TEX spellcheck = it-IT
% ------------------------------------------------------------------------ %
%
% ------------------------------------------------------------------------ %
% 	FIGURES COPYRIGHT
% ------------------------------------------------------------------------ %
%
\chapter{Figures Copyright}
%
\label{cap:figurescopyright}
%
% ------------------------------------------------------------------------ %
%
\section*{Chapter 2: State of Art}
\begin{itemize}

	\item Figures \ref{2.1:Categoriesofsmartobjects}, \ref{2.7:iotvswotprotocols}, \ref{2.8:iotvswotobjs}, \ref{2.10:newdivision} and \ref{2.11:foursublayers} are taken from \cite{guinard2011web} and reproduced with the kind authorization of the author, citing his personal website \url{http://dom.guinard.org}.
	
	\item Figures \ref{2.3:Rangeofdifferentnetworks} and \ref{2.5:bigdata5v} are reproduced with the kind authorization of DEIB, my department in Politecnico di Milano and its professors.
	
	\item Figure \ref{2.4:IPv4vsIPv6addresses} is a composition of two different images. Left part is subject to a public domain license. The license notice is available at \url{https://commons.wikimedia.org/wiki/File:Ipv4_address.svg}, which allows the reuse. Right part is subject to a public domain license. The license notice is available at \url{https://commons.wikimedia.org/wiki/File:Ipv6_address.svg}, which allows the reuse.
			
	\item Figure \ref{2.9:flyport} is taken and reproduced with the kind authorization of OpenPicus, \url{www.openpicus.com}.
	
\end{itemize}


\section*{Chapter 4: Solution}
\begin{itemize}

	\item Figure \ref{4.1: hap} are taken from the Apple WWDC 2014 informative pdf \url{http://devstreaming.apple.com/videos/wwdc/2014/701xx8n8ca3aq4j/701/701_designing_accessories_for_ios_and_os_x.pdf}, and according to \url{http://www.apple.com/legal/internet-services/terms/site.html} "Content" section, there is the possibility to reproduce the content, following the 4 points there listed.
	
	\item Figure \ref{4.4:semanticWeb} is subject to a public domain license. The license notice is available at \url{https://commons.wikimedia.org/wiki/File:RDF_example.svg}, which allows the reuse.
	
\end{itemize}
	

%

The images that are not explicitly listed are made by me and no copyright is needed.
 
% -----------------------------END------------------------------------- %